Better Corpus Visualization through Topic Ranking

### 2010-10-24 masters_thesis/topic_ranking_nips/paper.tex
Added some citations to the topic ranking paper

Topic modeling has been shown to be an effective means of extracting semantic
meaning from a collection of
documents~\cite{blei-2003-latent-dirichlet-allocation}.  Topic models have been
used as an inputs to other kinds of algorithms, such as classification and
sentiment tasks (cite some papers here), but the usefulness of topic models as
visualization tools in and of themselves has not been well established, and is
even in question (cite more papers).  Some recent work has been done in an
attempt to make corpus browsers using the results of LDA, and to make the
results of LDA more easily interpretable, but there is much work yet to be done
(still more citations).

>>>>

Topic modeling has been shown to be an effective means of extracting semantic
meaning from a collection of
documents~\cite{griffiths-2004-finding-scientific-topics}.  Topic models have
been used as an inputs to other kinds of algorithms, such as classification and
sentiment tasks~\cite{blei-2003-latent-dirichlet-allocation,
brody-2010-aspect-sentiment-model-for-reviews}, but the usefulness of topic
models as visualization tools in and of themselves has not been well
established, and is even in
question~\cite{newman-2010-visualizing-with-topic-maps}.  Some recent work has
been done in an attempt to make corpus browsers using the results of LDA, and
to make the results of LDA more easily interpretable, but there is much work
yet to be done~\cite{blei-arxiv-corpus-browser,
newman-2010-visualizing-with-topic-maps,
mei-2007-automatic-labeling-of-topic-models}.
